An efficient audio coding scheme for large scale acoustic monitoring

### 2017-06-11 paper/article.tex
Paper update + TOB filters fix

\ml{decrit ici les besoins avec une biblio}

\subsection{acoustic monitoring}

db spl, tiers d'octave, etc

10 refs

et dire que a partir de tiers d'ocatve 125 on peut retrouver tout les autres

\subsection{event detection}

15 refs

@@

As audio signals in the time domain offers very few, often inefficient processing possibilities to reduce data size, a common practice is to prefer the frequency domain which in many cases provides a better information representation. Therefore, we first apply a short-term Fourier transform (STFT) to the arbitrary-length signal (sampled continously in our application). The phase is then discarded, being mostly retrievable under certain conditions \cite{nawab1983}, as well as resulting negative frequency components which are redundant due to the real nature of studied signals. However, these operations do not induce a significant gain in data size compared to the raw audio. A solution is the implementation of auditory filterbanks to concentrate relevant information into a fixed number of values in the same way the human cochlea does, that is, grouping frequency coefficients around critical bands in a logarithmic scale. This technique offers an important advantage beyond the information-dimensionality ratio improvement: in the Fourier squared magnitude domain, it only amounts to a single matrix multiplication which can be reversed to some degree. In this work, we study two different filterbanks and propose a set of analysis parameters for each.\\

\ml{ce n'est pas vraiment ca. On a une contrainte qui est que l'on veut coder des données utilissables pour le monitoring acoustique et la reco d'evenements qui considère des représentations spécifiques. Je te propose donc de passer en revue les deux côtés dans la section ci dessus (background) et dire que nos choix sont raisonnables.}

We first use the widely known Mel scale as implemented by the \textit{rastamat} library \cite{ellis2005}. STFT analysis frames are obtained by applying a Hann window on 23.2~ms of signal with 50\% (11.6~ms) overlap to allow for phase recovery.\\

Another studied auditory transformation is the calculation of third-octave bands, generally used to compute the equivalent sound level $L_{eq}$ when acoustic measurements are needed. While the related filters are usually applied in the time domain, \cite{antoni2010} presents a frequency weights matrix design procedure that complies with both ANSI S1.1-1986 and IEC 61260-1:2014 standards, while respecting the partition of unity principle over all frequency bins in the relevant range. We implement this method for third-octave bands -17 to 13, ie. 20~Hz - 20kHz range, although with a minor change: inverting the use of sines and cosines is found to be a more intuitively correct approach, as we believe was the author's original intention. The STFT is computed for 125~ms audio windows, zero-padded to maximize FFT performance after the application of a rectangular function. No overlap is used to maximize the efficiency of the process as it is not needed to match the concept of "fast" acoustical measurements (8 per second). The rectangular window choice is made to ensure energy conservation in a given analysis frame. Results are compared with Couvreur's implementation \cite{couvreur}. We observe similar results and a better handling of sidemost bands: low frequencies where resolution is poor and higher frequencies where cutoff frequencies are superior than Nyquist's frequency rendering most time-domain filter designs difficult. \ml{pas clair}

\ml{mettre des chiffres ou une figure pour motiver ton choix dans la section dédiée et faire ici une ref}

@@

\ml{en general tes phrases sont trop longues. Coupe en deux des que tu peux et pas de paranthèses !!}

A Huffman coding scheme \cite{} is then used to further reduce data dimensionality. As in most entropy coding algorithms, the efficiency of this technique depends on two important factors: a reduced amount of symbols \ml{in the dictionnary ?} and a low data entropy \ml{explique ce dernier point}. The first is generally obtained by applying a quantization process to the signal, whereas the second is directly linked with the probability density function (PDF) of these symbols, with entropy decreasing when very few symbols have a very high probability of appearance. Considering an estimated PDF for our data as shown in Figure~\ref{fig:pdf}a, immediately applying a linear quantization clearly results in most of the information being lost. We therefore spread the PDF by taking the logarithm (natural or base 10) of the signal, then apply a linear quantization with $2^{q-1}-1$ output values to obtain Figure~\ref{fig:pdf}b. Finally, we use a $\Delta$-encoding algorithm \cite{} along the time dimension to reduce redundancies and effectively concentrate higher probabilities on symbols around zero (Figure~\ref{fig:pdf}c). This yields a higher amount of symbols at $2^q-1$ but a nevertheless smaller entropy. In the example shown here, the former is $H_{log} = 6.24~sh$ and the latter $H_{\Delta} = 3.54~sh$. Huffman encoding is then computed for texture frames of several minutes with a frame-specific symbol-code dictionnary. Indeed, we found that using a single dictionnary generated with an entire dataset was not beneficial in terms of efficiency or computation time. Alternatively, analysis frames can be encoded and sent separately for continous transfers using one general dictionnary.

\ml{a discuter. Pourquoi ne pas avoir un dic fixe, ce doit etre couteux de faire huffman a chaque fois ?}

\ml{ici encore, il faut mettre des chiffres pour motiver ce choix. plutot faire des refs a la subsection dediée}

\begin{figure*}[htbp]
	\centering
		\includegraphics[width=0.8\textwidth]{pdf.eps}
	\caption{Example of estimated probability density functions of the data throughout the encoding step. (left) Unchanged output of the representation step, concentrated towards very low values. (middle) PSD "flattening" effect induced by logarithm application. Here values are mapped to the range $[0, 2^7-1]$ and rounded to perform quantization. (right) Output of the $\Delta$ compression, with desirable probabilities as the input to a Huffman algorithm.}
	\label{fig:pdf}
\end{figure*}
6.24 before
3.54 after

@@

The entire coder process is summarized in Figure~\ref{fig:scheme}.

@@

\section{Evaluation}
A set of metrics is computed to assess the efficiency of the proposed coder scheme and determine the impact of the algorithm's parameters, which are as follow: the desired word size prior to Huffman encoding, set by quantization for both signal representation choices, and only for Mel bands the number of coefficients between 10 and 40. We also study the effect of time averaging analysis frames: to force a fixed amount of frames per second lesser than the average speech rate in phonemes per second is a possible way to alter intelligibility at the cost of temporal information resolution.\\

\subsection{efficiency}

detaille les resulats pour l'efficacité de codage

\subsection{recognition}

@@

We first evaluate the global loss of information by implementing the four classification models proposed in \cite{salamon2014}: a support vector machine with a radial basis function kernel, a random forest classifier with 500 trees, a decision tree and a k-nearest neighbors classifier with $k = 5$. Values for the SVM parameter $C$ and RBF kernel variance $\sigma^2$ are found with a grid search. We apply a discrete cosine transform to the critical band signal representation to obtain cepstra (known as Mel Frequency Cepstrum Coefficients or MFCC in the first case) of which we conserve the 25 first coefficients, and summarize along time with the mean, variance, skewness, kurtosis, minimum, maximum, median, derivative mean and variance, second order derivative mean and variance. The feature vector is thus comprised of 275 values to reproduce available results and compare with our own. Models are trained for each setup using the 10-fold method, that is, every combination of testing one fold on models trained with the other nine.\\

@@

	\ml{j'ai mis le paragraphe en dessous pour des raisons de clarté car cela ne fait pas parti du codeur. A reformuler}

 Recovering a linearly-scaled spectrogram can be achieved by scaling the transpose of the forward transformation matrix, although a loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}. Signal phase is approximated by either white noise spectrogram scaling or a Griffin\& Lim algorithm \cite{griffin1984}, and the signal is retrieved using overlap-add. When using overlap while computing third-octave bands, one can also avoid framing effects produced by rectangular windowing by convoluting the signal with another windowing function prior to inverse-STFT computation.\\

@@

The coder's output bitrate as well as additional measurement error is computed for both data representations, it is expressed in dB and compared to the IEC 61672-1:2013 standard on sound level meter tolerance. This is to verify that the quantization step yields a maximum absolute error inferior to the precision of the recording device. To provide relevant statistics, these quantities are estimated for a total of 53 10-minutes texture frames.\\

@@

\bibitem{nawab1983}
Nawab, H. and Quatieri, T. and Lim, J. (1983). Signal reconstruction from short-time Fourier transform magnitude. \textit{IEEE Transactions on Acoustics, Speech, and Signal Processing}, 31(4)

@@

>>>>

The present work is constrained to allow both acoustic monitoring and sound event recognition in urban soundscapes. Here we briefly review state-of-the-art methods in both subjects to guide our choices.

\subsection{Acoustic monitoring}

The considered sensor network primarily aims at monitoring urban soundscapes, that is, continously assessing their content and impact on the population. This is typically enabled by measuring energetic acoustic indicators such as the equivalent sound pressure level $L_{eq}$ in dB SPL or its A-weighted equivalent $L_{Aeq}$ in dBA. However, while these indicators have proven to correlate well with perceptual evaluations for negative impact sound environments \cite{gozalo2015}, they fail to fully describe soundscapes \cite{rychtarikova2013}. Many other variables can be derived to better account for previously implicit properties \cite{can2016} including percentile values or time evolution. Studies have been conducted to select relevant subsets of descriptors in sound environment characterization \cite{can2015, brocolini2013, nilsson2007}.\\

All the mentionned indicators are measured at periods ranging from 0.125~ms or 1~s (resp. fast and slow) to longer periods of several minutes. Therefore, sound frequency information remains unused despite being closely related with subjective evaluations \cite{ishiyama2000}. A simple solution is the calculation of energetic indicators for the 31 third-octave bands within the human audition range 20~Hz - 20~kHz.\\

This measurement appears well-suited for this work's purpose: in addition to being an efficient descriptor \cite{torija2013}, it allows for the computation of most cited indicators while representing reasonably small, fixed amounts of data to be transmitted.

\subsection{Event detection}

Another major interest of this work is sound event recognition. This problem has been the subject of extensive research in the past on speech \cite{anusuya2009}, music \cite{tzanetakis2002}, and lately more complex scenes in which the current work falls. Studied classification methods are diverse, ranging from time-dependant modeling with HMMs \cite{ntalampiras2014} to "bag-of-frames" approaches \cite{aucouturier2007, foggia2015}. Common architectures include learning-based classifiers such as support vector machines (SVM) \cite{kumar2016}, gaussian mixture models (GMM) \cite{radhakrishnan2005} or neural networks \cite{salamon2017, piczak2015}. However, the selection of relevant features is still an open debate. The most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal. Among them, mel spectrograms and their cepstral-domain derivation, the mel-frequency cepstrum coefficients (MFCC), are the most recurrent. These representations effectively try to model the human cochlear response to sounds by grouping frequency components around critical bands in a logarithmic scale, thus bearing important physical significance. They may also be exploited together with features computed in other domains to better model signal properties. For instance, \cite{cai2006} adds spectral features related to harmonicity and salient frequencies, and \cite{chu2009} uses a matching pursuit (MP) algorithm to deduce time-domaid features. Another promising solution is feature engineering via unsupervised learning, which \cite{salamon2015-2} implements with a k-means clustering technique. Alternative data representations such as the scattering transform \cite{bauge2013} show good results in environmental sound classification tasks \cite{salamon2015}.\\
A more detailed review of used methods is available in \cite{chachada2013}.

@@

The technical constraints of size inherent to the studied setup make it impossible to transmit raw audio recordings. Following the considerations briefly exposed in the previous section, we conclude that third-octave bands are a reasonable choice. As mentionned, they provide advantages in both acoustic monitoring and data volume per measurement period. The physical content is also close to that of mel spectrograms, being just another filterbank transform with logarithmic frequency scaling.\\

A common way to implement third-octave analysis is to first design the highest octave three filters, and use them on progressively time-decimated versions of the input signal \cite{davis1986}. In practice, however, this technique presents multiple issues. \cite{antoni2010} presents an alternative analysis method based on direct frequency weighting. The weights matrix design procedure complies with both ANSI S1.1-1986 and IEC 61260-1:2014 standards. It also respects the partition of unity principle over all frequency bins in the relevant range. Resulting filters for different parameter $l$ values are compared with Couvreur's implementation \cite{couvreur} of the time-domain filtering, as shown in Figure~\ref{fig:freq_filt}. The major difference is that gains at cutoff frequencies are fixed at the optimal -3dB by design.\\

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\columnwidth]{tob_imp.eps}
	\caption{Comparison of Couvreur's and Antoni's implementations of third-octave filters. Frequency-weighting allows for arbitrary transfer functions and thus more accurate gains as standards impose.}
	\label{fig:freq_filt}
\end{figure}

The first step is to represent the signal in the frequency domain using a short-term Fourier transform (STFT). The continuously sampled audio is segmented into 125~ms frames to provide "fast" acoustic measurements. The data is zero-passed to the next power of two to allow best fft performances. No overlap is used as it doubles both computational and memory costs and is not required for our application. A rectangular window is applied to ensure energy conservation in a given analysis frame. The phase is unimportant to third-octave analysis, thus it is discarded. Similarly, negative frequency components contain the same information as positive ones because the base signal is real. We then compute third-octave bands from the squared spectral magnitude by matrix multiplication with the frequency weights proposed in \cite{antoni2010} for $l = 2$\footnote{When implementing said method, we found that squaring the $\phi_l(p), l \geq 1$ intermediate function (p. 887) was the correct approach to meet cutoff frequencies requirements, and we believe this was the author's original intention.}. We include analysis for bands $i$ from -17 to 13, ie. center frequencies $f_i$ ranging from $20~Hz$ to $20~kHz$ with $f_0 = 1~kHz$. This means the main representation is composed of 31 values sampled every 125~ms.\\

Alternatively, we also implement the mel filterbank for testing purposes. Mel spectrograms can be used as a baseline method to evaluate the relative performance of third-octave bands in sound event recognition. Furthermore, this representation is not bound by constraints such as conservation of energy, specific framing parameters or fixed resolution. It offers a more flexible tool to study intelligibility alteration and coder performance, both of which we take interest in. Mel spectrograms are computed with the \textit{rastamat} library \cite{ellis2005}. STFT analysis frames are obtained by applying a Hann window on 23.2~ms of signal with 50\% (11.6~ms) overlap to allow for efficient phase recovery in further tests.

@@

A Huffman coding scheme \cite{huffman1952} is then used to further reduce data dimensionality. As in most entropy coding algorithms, the efficiency of this technique depends on two important factors. A reduced amount of symbols in the dictionnary yields smaller code size on lower probability symbols. Lower data entropy, ie. lower average information content of the signal distribution, also increases performance. The first is generally obtained by applying a quantization process to the signal, whereas the second is directly linked with the probability density function (PDF) of these symbols. It is defined as $H = -\sum\limits_i p_ilog_n(p_i)$, where $p_i$ is the probability of appearance of a given symbol and $n$ the numerical base in which information is represented. As such, entropy decreases when very few symbols have a very high probability of appearance and is maximum for a uniform distribution. Considering an estimated PDF for our data as shown in Figure~\ref{fig:pdf}a, immediately applying a linear quantization clearly results in most of the information being lost. We therefore spread the PDF by taking the logarithm of the representation. A linear quantization is then applied with $2^{q-1}-1$ output values to obtain Figure~\ref{fig:pdf}b. Finally, we use a $\Delta$-encoding algorithm along the time dimension to reduce redundancies. This also effectively concentrates higher probabilities on symbols around zero (Figure~\ref{fig:pdf}c). This yields a higher amount of symbols at $2^q-1$ but a nevertheless smaller entropy. In the example shown here, the former is $H_{log} = 6.24~sh$ and the latter $H_{\Delta} = 3.54~sh$. Huffman encoding is then computed with either a frame-specific symbol-code dictionnary or a constant one generated from an entire dataset. A comparison of both methods is shown in Figure~\ref{fig:dict_comp}. For most short texture frame durations, we found the local Huffman algorithm to be much faster. In fact, encoding complexity is function of the amount of dictionnary elements. If it is specific to a given data packet, then it does not need to contain every possible value. This gain seem to outweight the additional complexity induced by the tree generation algorithm. Alternatively, short texture frames or single analysis windows can be encoded using one general dictionnary to improve bitrate. This choice depends on which of the size and complexity parameters must be reduced most.\\

\begin{figure}[htbp]
	\centering
		\includegraphics[width=0.5\textwidth]{pdf.eps}
	\caption{Example of estimated probability density functions of the data throughout the encoding step. (left) Unchanged output of the representation step, concentrated towards very low values. (middle) PDF "flattening" effect induced by logarithm application. Here values are mapped to the range $[0, 2^7-1]$ and rounded to perform quantization. (right) Output of the $\Delta$ compression, with desirable probabilities as the input to a Huffman algorithm.}
	\label{fig:pdf}
\end{figure}

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\columnwidth]{dict_comp.eps}
	\caption{Performance comparison of locally and globally generated Huffman dictionnaries. (top) The mean execution time ratio favors the use of frame-specific dictionnaries for tested texture frame lengths. (bottom) The mean output bitrate is close for both algorithms, showing that the necessity of sending symbol-code pairs mostly compensates for their optimality.}
	\label{fig:dict_comp}
\end{figure}

@@

The entire coder scheme is summarized in Figure~\ref{fig:scheme}.

@@

\section{Evaluation}
A set of metrics is computed to assess the efficiency of the proposed coder scheme and determine the impact of the algorithm's parameters, which are as follow: the desired word size prior to Huffman encoding, set by quantization for both signal representation choices, and only for Mel bands the number of coefficients between 10 and 40. We also study the effect of time averaging analysis frames: to force a fixed amount of frames per second lesser than the average speech rate in phonemes per second is a possible way to alter intelligibility at the cost of temporal information resolution.

\subsection{Efficiency}

The coder's output bitrate as well as additional measurement error is computed for both data representations, it is expressed in dB and compared to the IEC 61672-1:2013 standard on sound level meter tolerance. This is to verify that the quantization step yields a maximum absolute error inferior to the precision of the recording device. To provide relevant statistics, these quantities are estimated for a total of 53 10-minutes texture frames.

\subsection{Event recognition}

@@

We first evaluate the global loss of information by implementing the four classification models proposed in \cite{salamon2014}: a support vector machine with a radial basis function kernel, a random forest classifier with 500 trees, a decision tree and a k-nearest neighbors classifier with $k = 5$. Values for the SVM parameter $C$ and RBF kernel variance $\sigma^2$ are found with a grid search. We apply a discrete cosine transform to the critical band signal representation to obtain cepstra (known as Mel Frequency Cepstrum Coefficients or MFCC in the first case) of which we conserve the 25 first coefficients, and summarize along time with the mean, variance, skewness, kurtosis, minimum, maximum, median, derivative mean and variance, second order derivative mean and variance. The feature vector is thus comprised of 275 values to reproduce available results and compare with our own. Models are trained for each setup using the 10-fold method, that is, every combination of testing one fold on models trained with the other nine.

@@

These metrics require a recovery of the time-domain signal. We must first recover a linearly-scaled spectrogram from the band-focused representations. This can be achieved by multiplying by the scaled transpose of the forward transformation matrix. A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}. Signal phase is approximated by either white noise spectrogram scaling or a Griffin\& Lim algorithm \cite{griffin1984}, and the signal is retrieved using overlap-add. When using overlap while computing third-octave bands, one can also avoid framing effects produced by rectangular windowing by convoluting the signal with another windowing function prior to inverse-STFT computation.\\

@@

@@

\bibitem{gozalo2015}
Rey Gozalo, G. and Trujillo Carmona, J. and Barrigon Morillas, J.M. and Gomez Escobar, V. (2015). Relationship between objective acoustic indices and subjective assessments for the quality of soundscapes. \textit{Applied Acoustics}, 97, pp. 1-10

\bibitem{rychtarikova2013}
Rychtarikova, M. and Vermeir, G. (2013). Soundscape categorization on the basis of objective acoustical parameters. \textit{Applied Acoustics}, 74(2), pp. 240-247

\bibitem{can2016}
Can, A. and Aumond, P. and Michel, S. and De Coensel, B. and Ribeiro, C. and Botteldooren, D. and Lavandier, C. (2016). Comparison of noise indicators in an urban context. In: \textit{Proceedings of the 45th International Congress and Exposition on Noise Control Engineering}, pp. 5678-5686

\bibitem{can2015}
Can, A. and Gauvreau, B. (2015). Describing and classifying urban sound environments with a relevant set of physical indicators. \textit{J. Ac. Soc. Am.}, 137(1), pp. 208-218

\bibitem{brocolini2013}
Brocolini, L. and Lavandier, C. and Quoy, M. and Ribeiro, C. (2013). Measurements of acoustic environments for urban soundscapes: Choice of homogeneous periods, optimization of durations, and selection of indicators. \textit{J. Ac. Soc. Am.}, 134(1), pp. 813-821

\bibitem{nilsson2007}
Nilsson, M. and Botteldooren, D. and De Coensel, B. (2007). Acoustic indicators of soundscape quality and noise annoyance in outdoor urban areas. In: \textit{Proceedings of the 19th International Congress on Acoustics}

\bibitem{ishiyama2000}
Ishiyama, T. and Hashimoto, T. (2000). The impact of sound quality on annoyance caused by road traffc noise: an influence of frequency spectra on annoyance. \textit{JSAE Review}, 21(2), pp. 225-230

\bibitem{torija2013}
Torija, A. and Ruiz, D. and Ramos-Ridao, A. (2013). Application of a methodology for categorizing and differentiating urban soundscapes using acoustical descriptors and semantic-differential attributes. \textit{J. Ac. Soc. Am.}, 134(1), pp. 791-802

\bibitem{anusuya2009}
Anusuya, M. and Katty, S. (2009).  Speech recognition by machine, a review. \textit{International Journal of Computer Science and Information Security}, 6(3), pp. 181-205

\bibitem{tzanetakis2002}
Tzanztakis, G. and Essl, G. and Cook, P. (2002). Automatic musical genre classification of audio signals. \textit{IEEE Transactions on Speech and Audio Processing}, 10(5), pp. 293-302

\bibitem{ntalampiras2014}
Ntalampiras, S. (2014). Universal background modeling for acoustic surveillance of urban traffic. \textit{Digital Signal Processing}, 31, pp. 69-78

\bibitem{aucouturier2007}
Aucouturier, J. and Defreville, B. and Pachet, F. (2007). The bag-of-frames approach to audio pattern recognition: A sufficient model for urban soundscapes but not for polyphonic music. \textit{J. Ac. Soc. Am.}, 122(2), pp. 881-891

\bibitem{foggia2015}
Foggia, P. and Petkov, N. and Saggese, A. and Strisciuglio, N. and Vento, M. (2015). Reliable detection of audio events in highly noisy environments. \textit{Pattern Recognition Letters}, 65, pp. 22-28

\bibitem{kumar2016}
Kumar, A. and Raj, B. (2016). Features and Kernels for Audio Event Recognition. \textit{arXiv Preprint}, Available at: \url{https://arxiv.org/abs/1607.05765}

\bibitem{radhakrishnan2005}
Radhakrishnan, R. and Divakaran, A. and Smaragdis, P. (2005). Audio analysis for surveillance applications. In: \textit{IEEE Workshop on Applications of Signal Processing to Audio and Acoustics}

\bibitem{salamon2017}
Salamon, J. and Bello, J. (2017). Deep convolutional neural networks and data augmentation for environmental sound classification. \textit{IEEE Signal Processing Letters}, 24(3), pp. 279-283

\bibitem{piczak2015}
Piczak, K. (2015). Environmental sound classification with convolutional neural networks. In: \textit{IEEE 25th International Workshop on Machine Learning for Signal Processing}

\bibitem{khunarsal2013}
Khunarsal, P. and Lursinsap, C. and Raicharoen, T. (2013). Very short time environmental sound classification based on spectrogram pattern matching. \textit{Information Sciences}, 243, pp. 57-74

\bibitem{couvreur2004}
Couvreur, L. and Laniray, M. (2004). Automatic noise recognition in urban environments based on artificial neural networks and hidden markov models. In: \textit{The 33rd International Congress and Exposition on Noise Control Engineering}

\bibitem{cai2006}
Cai, R. and Lu, L. and Hanjalic, A. and Zhang, H. and Cai, L. (2006). A flexible framewok for key audio effects detection and auditory context inference. \textit{IEEE Transactions on Audio, Speech, and Language Processing}, 14(3), pp. 1026-1039

\bibitem{chu2009}
Chu, S. and Narayanan, S. and Kuo, C. (2009). Environmental sound recognition with time-frequency audio features. \textit{IEEE Transactions on Audio, Speech, and Language Processing}, 17(6), pp. 1142-1158

\bibitem{salamon2015-2}
Salamon, J. and Bello, J. (2015). Unsupervised feature learning for urman sound classification. In: \textit{2015 IEEE International Conference on Acoustics, Speech and Signal Processing}

\bibitem{bauge2013}
Baugé, C. and Lagrange, M. and Andén, J. and Mallat, S. (2013). Representing environmental sounds using the separable scattering transform. In: \textit{2013 IEEE International Conference on Acoustics, Speech and Signal Processing}

\bibitem{salamon2015}
Salamon, J. and Bello, J. (2015). Feature learning with deep scattering for urban sound analysis. In: \textit{23rd European Signal Processing Conference}

\bibitem{chachada2013}
Chachada, S. and Kuo, C. (2013). Environmental sound recognition: A survey. In: \textit{2013 Asia-Pacific Signal and Information Processing Association Annual Summit and Conference}

\bibitem{davis1986}
Davis, S. (1986). Octave and fractional-octave band digital filtering based on the proposed ANSI standard. In: \textit{1986 IEEE International Conference on Acoustics, Speech and Signal Processing}

@@

\bibitem{huffman1952}
Huffman, D. (1952). A method for the construction of minimum-redundancy codes. \textit{Proceedings of the IRE}, 40(9), pp. 1098-1101
